Comparing Facebook's Prophet Forecasting to an ARIMA Model: A Diebold-Mariano Evaluation of the Top40 Index

### 2017-10-14 template/Draft_Paper.Rmd
All tables changed to r markdon tables

```{r ShortTable, results = 'asis'}

@@

```{r ForecastErrorStatisticsTable, results = 'asis'}

@@

The observations made from Table 2 in section 5.2.1 suggest that the ARIMA and Prophet models have equal predictive accuracy. These assertions can be formally quantified through a Diebold-Mariano(DM) test which evaluates whether the models have equal predictive accuracy against the alternative hypothesis that one model has superior accuracy over the other. Table 3 reports the results obtained when the rolling forecast errors were formally compared against each other over different time horizons.  
![](dm results.png){ width=105%}  
*Table 3 Results of the Diebold-Mariano Hypothesis Test*  
The p-value across all the time horizons for either linear and quadratic loss functions suggest that we would fail to reject the null hypothesis. This implies that the predictive accuracy of the models could be equal. These results formally validate the observations made obtained in section 5.2.1.

>>>>

```{r AIC Table for candidate ARIMA Models, results = 'asis'}

@@

```{r Forecast Error Statistics Table, results = 'asis'}

@@

The observations made from Table 2 in section 5.2.1 suggest that the ARIMA and Prophet models have equal predictive accuracy. These assertions can be formally quantified through a Diebold-Mariano(DM) test which evaluates whether the models have equal predictive accuracy against the alternative hypothesis that one model has superior accuracy over the other. Table 3 reports the results obtained when the rolling forecast errors were formally compared against each other over different time horizons.

```{r Table For Diebold Mariano Evaluation results, results = 'asis'}

col1 <- c("1"," ","5"," ","20"," ")
col2 <- rep(c("Linear","Quadratic"),3)
col3 <- c(0.553,0.128,0.691,0.334,'0.660',0.296)

dm.mat <- matrix(data = c(col1,col2,col3),ncol = 3)
dimnames(dm.mat) <- list(c(" "," "," "," "," "," "),   #row names
                          c("Forecast Horizon, h","Loss Function","P Value"))  #column names
dm.data = dm.mat %>% tbl_df()

dm.table <- xtable(dm.data, caption = "Results of the Diebold-Mariano Hypothesis Test for different loss functions")
  print.xtable(dm.table, 
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H', 
             # scalebox = 0.3, 
             comment = FALSE,
             include.rownames = getOption("xtable.include.rownames", FALSE), #exclude row number
             caption.placement = 'bottom'
             )

The p-value across all the time horizons for either linear and quadratic loss functions suggest that we would fail to reject the null hypothesis. This implies that the predictive accuracy of the models could be equal. These results formally validate the observations made obtained in section 5.2.1.

### 2017-10-14 template/Draft_Paper.tex
Tables in markdown, some, but not all plots in markdown, fixed issue with dates on figure 1, in-sample data with dplyr
All tables changed to r markdon tables

\includegraphics[width=1.00000\textwidth]{error stats.png}\\
\emph{Table 2 : Forecast error diagnostic statistics over different
forecasting horizons}

@@

The observations made from Table 2 in section 5.2.1 suggest that the
ARIMA and Prophet models have equal predictive accuracy. These
assertions can be formally quantified through a Diebold-Mariano(DM) test
which evaluates whether the models have equal predictive accuracy
against the alternative hypothesis that one model has superior accuracy
over the other. Table 3 reports the results obtained when the rolling
forecast errors were formally compared against each other over different
time horizons.\\
\includegraphics[width=1.05000\textwidth]{dm results.png}\\
\emph{Table 3 Results of the Diebold-Mariano Hypothesis Test}\\
The p-value across all the time horizons for either linear and quadratic
loss functions suggest that we would fail to reject the null hypothesis.
This implies that the predictive accuracy of the models could be equal.
These results formally validate the observations made obtained in
section 5.2.1.

>>>>

@@

The observations made from Table 2 in section 5.2.1 suggest that the
ARIMA and Prophet models have equal predictive accuracy. These
assertions can be formally quantified through a Diebold-Mariano(DM) test
which evaluates whether the models have equal predictive accuracy
against the alternative hypothesis that one model has superior accuracy
over the other. Table 3 reports the results obtained when the rolling
forecast errors were formally compared against each other over different
time horizons.

\begin{table}[H]
\centering
\begin{tabular}{lll}
  \hline
Forecast Horizon, h & Loss Function & P Value \\ 
  \hline
1 & Linear & 0.553 \\ 
    & Quadratic & 0.128 \\ 
  5 & Linear & 0.691 \\ 
    & Quadratic & 0.334 \\ 
  20 & Linear & 0.660 \\ 
    & Quadratic & 0.296 \\ 
   \hline
\end{tabular}
\caption{Results of the Diebold-Mariano Hypothesis Test for different loss functions} 
\end{table}

The p-value across all the time horizons for either linear and quadratic
loss functions suggest that we would fail to reject the null hypothesis.
This implies that the predictive accuracy of the models could be equal.
These results formally validate the observations made obtained in
section 5.2.1.
